Plant-pollintor networks worldwide are composed by the same specific building

### 2021-10-15 Draft/Draft.Rmd
working again with paragraph 3 not happy with the ending

From a pollinator perpective, we found that generalist network motifs were consistently over-represented (**Figure 2**). For instance, when we compare motifs with equal structure but inverted, we found that floral visitors had always over-representation in the positions that implied the highest number of links. Despite this is in good agreement with the current view of the generalist tendency of pollinators [@waser1996; @olesen2002; @ollerton2017], we found that this over-representation of the generalist network motifs was largely driven by the functional group of bees (e.g., positions 42, 46, 16, 4, 14 and 35 in motifs 15, 17, 7, 2, 6 and 13, respectively; see **Figure 3** for positions and **Figure 4** for motifs) while the rest of the groups tended to be under-represented in these generalist motifs and over-represented in motif positions with specialist roles (e.g., positions 11, 21, 28 and 34 in motifs 5, 9, 11 and 13, respectively; see **Figure 3** for positions and **Figure 4** for motifs). This large effect of bees on the overall patterns, are no surprise as bees were the functional group with largest number of interaction records in the whole set of networks as also recorded for other broad scale plant-pollinator network studies [@carvalheiro2014; @ollerton2017]. Unlike floral visitors, plant functional groups showed little differences between their maximum and minimum percentile on the different motif positions in the comparison with simulated networks, and thus similar probability of appearing on them. However, the groups that involved higher levels of outcrossing showed a tendency to be more over-represented and probable on the different motif positions. For instance, the group of self incompatible perennials with large flowers, one of the groups that is expected to have higher levels of outcrossing rate [@goodwillie2010], showed the highest over-representation of all plant functional groups (**Figure 3**); and the group of tall plants with unisexual flowers, the one that is expected to have the highest dependence of pollinators on reproduction [@rodger2021], was the most probable on the generalist motif for plant positions (i.e, plant nodes with 3 to 4 links).

The observed functional group probabilities on the different motif positions (**Figure 4**) were insufficient to predict most of the observed network motifs (**Figure 5**). This implies that not just the representation of network motifs types but also the identity of the elements of their structure is influenced by ecological processes that determine under- and over-representation of the different motif combinations. In addition, we found that just 30% of the possible 5,3250 motif combinations took place. As suggested by @simmons2020, exploring the proportion of competitive or facilitative relized indirect interactions is a necessesary next step to improve our understanding of the architecture of biodiversity [@bascompte2007]. In addition, this restricted set of possible combinations is no surprise, because plant-pollinator networks (i.e., full network level) have a high percentage of non-realized interactions [@jordano2003; @bascompte2013]. Some of this non-observed motif combinations are likely to be the cause of under-sampling [@olesen2011; @jordano2016]. However, a large portion of the possible interactions do not take place because of life history constraints [i.e., forbidden links; @olesen2011; @bartomeus2016; @jordano2016]. Thus, similarly to the presence of forbidden links at the network level, we found also the existence of forbidden motifs that represented non-realized combinations of indirect interactions.

>>>>

From a pollinator perpective, we found that generalist network motifs were consistently over-represented (**Figure 2**). For instance, when we compare motifs with equal structure but inverted, we found that floral visitors had always over-representation in the positions that implied the highest number of links. Despite this is in good agreement with the current view of the generalist tendency of pollinators [@waser1996; @olesen2002; @ollerton2017], we found that this over-representation of the generalist network motifs was largely driven by the functional group of bees (e.g., positions 42, 46, 16, 4, 14 and 35 in motifs 15, 17, 7, 2, 6 and 13, respectively; see **Figure 3** for positions and **Figure 4** for motifs) while the rest of the functional groups tended to be under-represented in these generalist motifs and over-represented in motif positions with specialist roles (e.g., positions 11, 21, 28 and 34 in motifs 5, 9, 11 and 13, respectively; see **Figure 3** for positions and **Figure 4** for motifs). This large effect of bees on the overall patterns is no surprise, as bees were the functional group with largest number of interaction records in the whole set of networks as also recorded for other broad scale plant-pollinator network studies [@carvalheiro2014; @ollerton2017]. Unlike floral visitors, plant functional groups showed little differences between their maximum and minimum percentile on the different motif positions in the comparison with simulated networks, and thus similar probability of appearing on them. However, the groups that involved higher levels of outcrossing showed a tendency to be more over-represented and probable on the different motif positions. For instance, the group of self incompatible perennials with large flowers, one of the groups that is expected to have higher levels of outcrossing rate [@goodwillie2010], showed the highest over-representation of all plant functional groups (**Figure 3**); and the group of tall plants with unisexual flowers, the one that is expected to have the highest dependence of pollinators on reproduction [@rodger2021], was the most probable on the generalist motif for plant positions (i.e, plant nodes with 3 to 4 links).

The observed functional group probabilities on the different motif positions (**Figure 4**) were insufficient to predict most of the observed network motifs (**Figure 5**). This implies that not just the representation of network motifs types but also the identity of the elements of their structure is influenced by ecological processes that determine under- and over-representation of the different motif combinations. As suggested by @simmons2020, exploring the proportion of these realized network motifs that is competitive or facilitative is a necessary next step to improve our understanding of the architecture of biodiversity [@bascompte2007]. In addition, we found that just 30% of the possible 5,3250 motif combinations took place. This concurs well with the general idea that plant-pollinator networks have a high porportion of non-realized interactions [@jordano2003; @bascompte2013] which can be also infered to indirect interactions. @olesen2011 also found a similar porportion of non-realized links in comparison with our findings of non-realized indirect interactions (80% and 70%, respectively). Some of this non-observed interactions are propably caused by under-sampling [@olesen2011; @jordano2016]. However, a large portion of the possible interactions do not take place because of life history constraints [i.e., forbidden links; @olesen2011; @bartomeus2016; @jordano2016]. Thus, similarly to the presence of forbidden links at the network level, we also found the existence of forbidden motifs that represented almost two thirds of the total combinations of indirect interactions.

I NEED A LAST PHRASE HERE

Despite the recent efforts in understanding what are the main drivers of plant-pollinator interactions that ultimately shape competitive and facilitative processes, we lack comprehensive understanding of how these processes affect species direct and ultimately indirect interactions at a macroecological scale.
